The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-09-22 paper2_JNLS/paper.tex
NM

% Later: Plot of transfer function for different lambdas. Shows that the transfer function is relatively insensitive to truncation index, as long as N scales appropriately.

>>>>

% Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/transfig.pdf}
\caption{
stuff
}
\label{transfig}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

Figure \ref{transfig}(a) shows the transfer function $\thdn = \transf(\thup)$ that results from the statistical matching condition \eqref{statmatch}, for an incoming inverse temperature in the range $\thup \in [0,20]$. In this figure, all model parameters are set by their experimental values, and we show the cases $\Lambda = 8, 16, 32$ with $\lamfac = \Lambda/2$ in each. As seen here, the transfer function is relatively insensitive to the truncation index since all three curves are relatively close to one another. This insensitivity is a consequence of scaling $\lamfac$ with $\Lambda$ appropriately as discussed previously.

Next, Fig.~\ref{transfig}(b) shows the skewness of the incoming (green) and outgoing (blue) wave fields, as they depends on the incoming inverse temperature $\thup$. In line with experimental observations, the incoming skewness is small (always less than 0.2), while the outgoing wave skewness is much higher. Specifically, to capture the experimentally observed peak skewness of about 0.7, we can choose the value of $\thup$ in the range 10--15.
